Investigating Overfitting in Convolutional Neural Networks

### 2025-05-20 paper.tex
fixed margins

% Packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{float}
\usepackage{tikz}
\usepackage{setspace}
\usepackage{times}

@@

    \noindent\textbf{Hypotheses}\newline
    $H_0: \beta = 0$ \newline
    $H_a: \beta > 0$ \newline\newline
    Where $\beta$ is the true slope of the population least‐squares regression line that relates number
    of parameters of the model to the difference in accuracy of the model on the train dataset and the
    test dataset.

@@

    We trained $\mathbf{x}$ convolutional models on a randomly selected small subset of size 100 images
    from the CIFAR-10 dataset, each with the same architecture (\textit{see figure 1}). Each model had
    a different number of parameters, roughly uniformly ranging from approximately 1 million to 50 million.
    For each model, the initial values of the parameters are randomly set, so each model can be seen as randomly
    selected from all possible models of that size and architecture before training.

    \noindent\textbf{Model Architecture}
    \begin{center}
        \begin{tikzpicture}[node distance=4mm and 0mm]
            \node[layer=gray!10]                     (input)  {Input $(32\times32\times3)$};
            \node[layer=blue!10,  below=of input]    (conv1)  {Conv2D: $32n$ filters, $3\times3$, ReLU};
            \node[layer=cyan!10,  below=of conv1]    (pool1)  {MaxPool: $2\times2$};
            \node[layer=blue!10,  below=of pool1]    (conv2)  {Conv2D: $64n$ filters, $3\times3$, ReLU};
            \node[layer=cyan!10,  below=of conv2]    (pool2)  {MaxPool: $2\times2$};
            \node[layer=orange!10,below=of pool2]    (flat)   {Flatten};
            \node[layer=green!15, below=of flat]    (dense1) {Dense: $128n$, ReLU};
            \node[layer=green!15, below=of dense1]  (dense2) {Dense: $64n$, ReLU};
            \node[layer=red!15,   below=of dense2]  (output) {Dense (Output): 10, Softmax};

@@

    \centerline{\textit{Figure 1: Architecture of CNN Model}}

>>>>

% Packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{float}
\usepackage{tikz}
\usepackage{setspace}
\usepackage{times}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}

@@

    \noindent\textbf{Hypotheses:}\newline
    \centerline{$H_0: \beta = 0$} \newline
    \centerline{$H_a: \beta > 0$} \newline
    Where $\beta$ is the true slope of the population least‐squares regression line that relates number
    of parameters of the model to the difference in accuracy of the model on the train dataset and the
    test dataset.

@@

    We trained $\mathbf{x}$ convolutional models on a randomly selected small subset of size 100 images
    from the CIFAR-10 dataset, each with the same architecture (\textit{see figure 1}). Each model had
    a different number of parameters, roughly uniformly ranging from approximately 1 million to 50 million.
    We controlled the parameter count by multiplying the amount of filters for the Conv2D layers and the amount of units
    for the hidden Dense layers by a scalar factor, $n$.
    For each model, the initial values of the parameters are randomly set, so each model can be seen as randomly
    selected from all possible models of that size and architecture before training.

    \noindent\textbf{Model Architecture}
    \begin{center}
        \begin{tikzpicture}[node distance=4mm and 0mm]
            \node[layer=gray!10]                     (input)  {Input $(32\times32\times3)$};
            \node[layer=blue!10,  below=of input]    (conv1)  {Conv2D: $32n$ filters, $3\times3$, ReLU};
            \node[layer=cyan!10,  below=of conv1]    (pool1)  {MaxPool: $2\times2$};
            \node[layer=blue!10,  below=of pool1]    (conv2)  {Conv2D: $64n$ filters, $3\times3$, ReLU};
            \node[layer=cyan!10,  below=of conv2]    (pool2)  {MaxPool: $2\times2$};
            \node[layer=orange!10,below=of pool2]    (flat)   {Flatten};
            \node[layer=green!15, below=of flat]    (dense1) {Dense: $128n$ units, ReLU};
            \node[layer=green!15, below=of dense1]  (dense2) {Dense: $64n$ units, ReLU};
            \node[layer=red!15,   below=of dense2]  (output) {Dense (Output): 10, Softmax};

@@

    \centerline{\textit{Figure 1: General Architecture of Our Models}}
